Tactics and Marks in Banach Mazur Games

### 2018-02-22 postdoctoral/k-markov-tactic-banach-mazur.tex
finish proof for improving (k+2)-mark to (k+2)-tactic

  \begin{proof}
    Let \(\sigma\) witness \(\plII\kmarkwin{(k+2)}\bmPoGame{\mb P}{W}\).
    Define \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\) for \(t\in\mb P^1\).
    Since \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\leq a_{t(0)}(0)\leq t(0)\),
    this is a legal move.

@@

    Let \(f\) be a legal attack against \(\tau\). The intuition of the
    following proof is simple: by construction, \(l_t\) will produce
    the number of \(\plI\)'s moves forgotten by \(\plII\)'s \((k+2)\)-tactic,
    allowing the \((k+2)\)-tactic to deduce the round number and thus exploit
    the winning \((k+2)\)-mark.

    We may quickly verify
    that \(l_{f\rest 2}=0\) since
    \[
      (f\rest 2)(1)
        =
      f(1)
        \leq
      \tau(f\rest 1)
        =
      \sigma(\<a_{f(0)}(0)\>,1)
        \leq
      a_{f(0)}(0)
        =
      a_{(f\rest 2)(0)}(0+0)
    .\]
    We claim in general that \(l_{f\rest(j+2)}=0\) for \(j\leq k\).
    Assuming \(l_{f\rest(j+2)}=0\) for \(j<k\),
    \[
      (f\rest(j+3))(j+2)
        =
      f(j+2)
        \leq
      \tau(f\rest(j+2))
        =
      \sigma(f\rest(j+2)',0+j+2)
        \leq
      f\rest(j+2)'(j+1)
    \]
    \[
        =
      a_{(f\rest(j+2))(j+1)}(j+1)
        =
      a_{(f\rest(j+3))(j+1)}(0+(j+1))
    \]
    proving \(l_{f\rest(j+3)}=0\).

    Now we show that \(l_{f\rest(j+2)\last(k+2)}=j-k\) for \(j\geq k\).
    We've just shown that this is true for our base case \(j=k\).
    Now assuming \(l_{f\rest(j+2)\last(k+2)}=j-k\), we show...
  \end{proof}

>>>>

  \begin{proof}
    The intuition of the following proof is simple: consider the case
    \(k=0\). During the first round,
    \(\plI\) plays some \(p_0\in\mb P\), and
    \(\plII\) can store the round number \(0\) (known by \(\plII\) since they
    only have knowledge of one move) by pretending \(\plI\) chose
    \(a_{p_0}(0)\leq p_0\) instead, and applying the winning \(2\)-mark.
    Thus when \(\plI\) plays \(p_1\leq a_{p_0}(0)\), \(\plII\) will have
    knowledge of both \(p_0\) and \(p_1\), and thus can observe that as
    \(p_1\leq a_{p_0}(0)\), it must be round \(1\) rather than some future
    round, and can repeat this process by pretending \(\plI\) chose
    \(a_{p_1}(1)\leq p_1\) and \(a_{p_0}(0)\leq p_0\) instead.

    We now proceed with a formal proof.
    Let \(\sigma\) witness \(\plII\kmarkwin{(k+2)}\bmPoGame{\mb P}{W}\).
    Define \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\) for \(t\in\mb P^1\).
    Since \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\leq a_{t(0)}(0)\leq t(0)\),
    this is a legal move.

@@

    Let \(f\) be a legal attack against \(\tau\).
    We may quickly verify
    that \(l_{f\rest 2}=0\) since
    \begin{align*}
      (f\rest 2)(1)
        &=
      f(1)
        \\&\leq
      \tau(f\rest 1)
        \\&=
      \sigma(\<a_{f(0)}(0)\>,1)
        \\&\leq
      a_{f(0)}(0)
        \\&=
      a_{(f\rest 2)(0)}(0+0)
    \end{align*}
    We claim in general that \(l_{f\rest(j+2)}=0\) for \(j\leq k\).
    Assuming \(l_{f\rest(j+2)}=0\) for \(j<k\),
    \begin{align*}
      (f\rest(j+3))(j+2)
        &=
      f(j+2)
        \\&\leq
      \tau(f\rest(j+2))
        \\&=
      \sigma(f\rest(j+2)',0+(j+2))
        \\&\leq
      f\rest(j+2)'(j+1)
        \\&=
      a_{(f\rest(j+2))(j+1)}(0+(j+1))
        \\&=
      a_{(f\rest(j+3))(j+1)}(0+(j+1))
    \end{align*}
    proving \(l_{f\rest(j+3)}=0\).

    Now we show that \(l_{f\rest(n+2)\last(k+2)}=j-k\) for \(n\geq k\).
    We've just shown that this is true for our base case \(n=k\)
    since in that case \(f\rest(n+2)\last(k+2)=f\rest(k+2)\).
    Now assuming \(l_{f\rest(n+2)\last(k+2)}=n-k\) for some \(n\geq k\),
    we observe
    \begin{align*}
      (f\rest(n+3)\last(k+2))(k+1)
        &=
      f(n+2)
        \\&\leq
      \tau(f\rest(n+2)\last(k+2))
        \\&=
      \sigma((f\rest(n+2)\last(k+2))',(n-k)+(k+2))
        \\&\leq
      (f\rest(n+2)\last(k+2))'(k+1)
        \\&=
      a_{(f\rest(n+2)\last(k+2))(k+1)}((n-k)+(k+1))
        \\&=
      a_{(f\rest(n+3)\last(k+2))(k)}((n+1-k)+(k))
    \end{align*}
    and conclude \(l_{f\rest(n+3)\last(k+2)}=n+1-k\).

    Define \(g\in\mb P^\downarrow\) by \(g(0)=f(0)\) and
    \(g(j+1)=a_{f(j+1)}(j+1)\).
    Reviewing the above, the reader may confirm that we have shown for
    \(n<k+2\)
    \[
      f(n+1)
        \leq
      \tau(f\rest(n+1))
        =
      \sigma(g\rest(n+1),n+1)
        \leq
      g(n)
        \leq
      f(n)
    \]
    and for \(n\geq k+2\)
    \[
      f(n+1)
        \leq
      \tau(f\rest(n+1)\last(k+2))
        =
      \sigma(g\rest(n+1)\last(k+2),n+1)
        \leq
      g(n)
        \leq
      f(n)
    \]
    Thus \(g\) is a legal attack against \(\sigma\), and since \(\sigma\)
    is winning, \(g\in W\). Since \(W\) is closed under zipping,
    \(f\in W\), and therefore \(\tau\) is also winning.
  \end{proof}
